Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
generate doc

In total, 12 of 29 collared female caribou swam between islands in the Fogo
Island archipelago. On average, caribou swam approximately `r neventidMean`
(range = `r neventidMin`-`r neventidMax`) times per year and remained on each
island for approximately `r dur` (range = `r durMin`-`r durMax`) days before
swimming again. Based on swimming data, we separated the population into three
apparent groups of individuals: those that swam regularly between islands (n =
3, every ~`r indMean days`); those that rarely engaged in swimming events (n =
9, every ~ `r ind2Mean days`); and those that never swam (n = 17).

>>>>

In total, 12 of 29 collared female caribou swam between islands in the Fogo
Island archipelago. On average, caribou swam approximately `r neventidMean`
(range = `r neventidMin`-`r neventidMax`) times per year and remained on each
island for approximately `r dur` (range = `r durMin`-`r durMax`) days before
swimming again. Based on swimming data, we separated the population into three
apparent groups of individuals: those that swam regularly between islands (n =
3, every ~`r indMean` days); those that rarely engaged in swimming events (n =
9, every ~ `r ind2Mean` days); and those that never swam (n = 17).
